A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-07 paper.tex
clarify calculation and update intro text for steves comment

While \glspl{iam} are implemented in myriad ways\footnote{IAM models are
  numerous and have a long history in the scientific literature. Various IAMs
  have collaborated to produce
  \href{http://themasites.pbl.nl/models/advance/index.php/ADVANCE_wiki}{community
    IAM documentation} which readers can access for a full treatment of model
  implementation and features.}, including simulation and optimization, the core
inputs and outputs are similar across different models. Modeling teams
incorporate data on energy systems, land use, economics, demographics and
emissions sources and concentrations, among other data, in order to provide
consistent existing trajectories of modeled variables. The models then provide
estimates of future trajectories of these variables under various socio-economic
and technological assumptions as well as proposed policy constraints, e.g.,
targets for future \gls{ghg} emissions.

@@

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs (Figure
\ref{fig:regions}); harmonization is performed directly on the native regional
spatial resolution. Historical data is taken from previously described \gls{luc}
and anthropogenic sources, which comprise 10 separate pollutant and \gls{ghg}
species and 12 sectors shown in Table \ref{tab:sp}. A total of 970 distinct
trajectories were harmonized for each scenario, and therefore 1940 trajectories
were harmonized in total for these two illustrative scenarios.  \noxx generated
from the Energy sector provides an example of an emissions species and sector in
which all regions were satisfactorily harmonized with the default
methods. Figure \ref{fig:nox} shows the results of harmonization in Asia, and
Table \ref{tab:nox} describes the parameters that underlie the choice of method
for each harmonized trajectory. Importantly, the default methods provide
regional trajectories for both the reference and mitigation scenarios that match
the general unharmonized model behavior and also result in global aggregated
emissions that are similar to the unharmonized trajectory.

>>>>

While \glspl{iam} are implemented in myriad ways\footnote{IAM models are
  numerous and have a long history in the scientific literature. Various IAMs
  have collaborated to produce
  \href{http://themasites.pbl.nl/models/advance/index.php/ADVANCE_wiki}{community
    IAM documentation} which readers can access for a full treatment of model
  implementation and features.}, including simulation and optimization, the core
inputs and outputs are similar across different models. Modeling teams
incorporate data on energy systems, land use, economics, demographics and
emissions sources and concentrations, among other data, in order to provide a
consistent starting point for future projections. The models then provide
estimates of future trajectories of these variables under various socio-economic
and technological assumptions as well as proposed policy constraints, e.g.,
targets for future \gls{ghg} emissions.

@@

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs (Figure
\ref{fig:regions}); harmonization is performed directly on the native regional
spatial resolution. Historical data is taken from previously described \gls{luc}
and anthropogenic sources, which comprise 10 separate pollutant and \gls{ghg}
species and 12 sectors shown in Table \ref{tab:sp}. A total of 970 distinct
trajectories\footnote{Table \ref{tab:sp} compiles 24 global trajectories and 86
  regional trajectories. Therefore, with 11 model regions, 970 total
  trajectories are harmonized.} were harmonized for each scenario, and therefore
1940 trajectories were harmonized in total for these two illustrative scenarios.
\noxx generated from the Energy sector provides an example of an emissions
species and sector in which all regions were satisfactorily harmonized with the
default methods. Figure \ref{fig:nox} shows the results of harmonization in
Asia, and Table \ref{tab:nox} describes the parameters that underlie the choice
of method for each harmonized trajectory. Importantly, the default methods
provide regional trajectories for both the reference and mitigation scenarios
that match the general unharmonized model behavior and also result in global
aggregated emissions that are similar to the unharmonized trajectory.
